Data Preparation

### 2019-03-11 Data Preparation.Rmd
filter out terms composed of 1 or 2 letters
split big chunk that cleans student data into three smaller chunks for clarity

  data %>%
    anti_join(
      stop_words,
      by = "word"
      ) %>%
    anti_join(
      sw_own,
      by = "word"
      )

@@

Our dataframe contains many variables and rows that are either empty or meaningless for our analysis. First, we filter, the final grades of studets to keep only relevant rows (Final Confirmed Grades are those with `Appraisal (Description)` as "Grade supervisor"). Then we select ony the 10 variables that we will use for the anlysis, and give them more comprehensible names.
```{r}
#
# Set up
UCM_course <- d_text$overview$`Course ID` %>%
  unique %>% 
  paste(collapse = "|")

# helper function
is_offered_at_UCM <- function(x) x %>% str_detect(UCM_course)

@@

  # The dataset has multiple rows for each student - course following guidelines of Richard Vos, we only consider: `Appraisal (Description)` == "Grade supervisor" and `Appraisal Type` == "7055"
  filter(
    `Appraisal (Description)` == "Grade supervisor",
    `Appraisal Type`          == "7055" # removes ~ 15 observations
  ) %>%

  # Select: Student ID, course ID, when course taken and grade 
  select(
    `Student ID`   = `Student Number`,
    `Course ID`    = `Module (Abbrev.)`,
    Year_numerical =`Academic Year`,
    Period         = `Academic Session`,
    Grade          = `Grade symbol`
  ) %>%

@@

  select(
    - Year_numerical,
    - Period
    ) %>%

  add_count(
    `Student ID`, `Course ID`, time,
    sort = TRUE
    ) %>%
  print

  # if student took resit (recorder in same year and period !!!NOT TRUE!!!), only keep failing grade 
  # group_by(
  #   `Student ID`,
  #   `Course ID`,
  #   Year,
  #   Period
  #   ) %>%
  # summarize(
  #   Grade = min(Grade)
  #   ) %>%
  # ungroup
```

>>>>

  data %>%
    anti_join(
      stop_words,
      by = "word"
      ) %>%
    anti_join(
      sw_own,
      by = "word"
      ) %>%
    filter(
      nchar(word) > 2
      )

@@

Our dataframe contains many variables and rows that are either empty or meaningless for our analysis. First, we filter, the final grades of studets to keep only relevant rows (Final Confirmed Grades are those with `Appraisal (Description)` as "Grade supervisor"). Then we select ony the 10 variables that we will use for the anlysis, and give them more comprehensible names.

```{r}
#
# Set up
UCM_course <- d_text$overview$`Course ID` %>%
  unique %>% 
  paste(collapse = "|")

# helper function
is_offered_at_UCM <- function(x) x %>% str_detect(UCM_course)
```

```{r}
d_transcript <- d_transcript %>%

  # The dataset has multiple rows for each student - course. Following guidelines of Richard Vos, we only consider: `Appraisal (Description)` == "Grade supervisor" and `Appraisal Type` == "7055"
  filter(
    `Appraisal (Description)` == "Grade supervisor",
    `Appraisal Type`          == "7055" # removes ~ 15 observations
  )
```

```{r}
d_transcript <- d_transcript %>%

  # Select: Student ID, course ID, when course taken and grade 
  select(
    `Student ID`   = `Student Number`,
    `Course ID`    = `Module (Abbrev.)`,
    Year_numerical =`Academic Year`,
    Period         = `Academic Session`,
    Grade          = `Grade symbol`
  )
```

```{r}

@@

@@

  select(
    - Year_numerical,
    - Period
    )
```

```{r}
d_transcript %>%

  # highlight issue: there are several rows with unique student ID - course ID - time combination.
  add_count(
    `Student ID`, `Course ID`, time,
    sort = TRUE
    ) %>%
  print
```
